Exploratory Analysis

### 2023-11-30 Code/Draft1Rmd.Rmd
Update Draft1Rmd.Rmd

A synthetic control analysis was conducted using Washington and Oregon as donor states. This analysis has significant limitations due to the lack of donor states and potential lack of credible covariates.

## Difference-in-Difference 
We used a difference-in-difference regression with fixed effects to investigate the impact of drug decriminalization in Oregon counties compared to other states.

@@

### Synthetic Control 
```{r results="hide"}
#Synthetic Control

>>>>

## Difference-in-Difference 
We used a difference-in-difference regression with fixed effects to investigate the impact of drug decriminalization starting in 2021 in Oregon counties compared to other states. The treatment effect shows a 80.39 decrease in overdose deaths compared to the control group and is statistically significant (p < 0.001). The fixed effects for years 2019 onwards are statistically signifcant, which indicate a time trend.

@@

### Synthetic Control 
A synthetic control analysis was conducted using Washington and Oregon as donor states. This analysis has significant limitations due to the lack of donor states and potential lack of credible covariates.

```{r results="hide"}
#Synthetic Control
